### 2021-04-12 priority-cp.tex
Remove instances of \cite as noun.

The main change we make to PCP is \emph{removing commuting conversions} and defining an operational semantics based on structural congruence. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut (or cycle in \cite{dardhagay18}) elimination.
However, from the perspective of process calculi, commuting conversions behave strangely: they allow an input/output action to be moved to the top of a process, thus potentially blocking actions which were previously possible (an example is given in \cref{app:commuting-conversions}). This makes CP, and PCP in \cite{dardhagay18}, non-confluent.
As Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, if using structural congruence.
%Consider the commuting conversion $(\kappa_{\parr})$ for $\pcp{\tm{\recv{x}{y}{P}}}$:
%\begin{mathpar}
%  (\kappa_{\parr})
%  \quad
%  \tm{\res{z}{z'}{(\ppar{\recv{x}{y}{P}}{Q})}}
%  \red
%  \tm{\recv{x}{y}{\res{z}{z'}{(\ppar{P}{Q})}}}
%\end{mathpar}
%As a result of $(\kappa_{\parr})$, $\pcp{\tm{Q}}$ becomes blocked on $\pcp{\tm{\labrecv{x}{y}}}$, and any actions $\pcp{\tm{Q}}$ was able to perform become unavailable. Consequently, CP is non-confluent:
%\begin{mathpar}
%  \setlength{\arraycolsep}{2em}
%  \begin{array}{cc}
%    \multicolumn{2}{c}{%
%    \hspace*{10ex}
%    {\tm{\res{x}{x'}{(\ppar{\recv{a}{y}{P}}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    \\
%    \qquad\rotatebox[origin=c]{270}{$\red\hphantom{{}^+}$}
%    &
%    \rotatebox[origin=c]{270}{$\red^+$}\qquad
%    \\
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    &
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{Q})}}}}
%  \end{array}
%\end{mathpar}
%

@@

We prove closed progress for our updated PCP. The proof is in \cref{prf:thm-pcp-closed-progress}.
\begin{compacttheorems}
  \begin{restatabletheorem}{thmpcpclosedprogress}[Progress, $\pcp{\red}$]
    \label{thm:pcp-closed-progress}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\emptyenv}}$, then either $\pcp{\tm{P}=\tm{\halt}}$ or there exists a $\pcp{\tm{Q}}$ such that $\pcp{\tm{P}\red\tm{Q}}$.
  \end{restatabletheorem}
\end{compacttheorems}
\endgroup

@@

%\noindent
%\textbf{Milner's Cyclic Scheduler}.
%As an example of a deadlock-free cyclic process, Dardha and Gay~\cite{dardhagay18} introduce an implementation of Milner's cyclic scheduler~\cite{milner89} in Priority CP. We have reproduced the scheduler in our updated PCP, and showed its translation to PGV. Full details are given in \cref{sec:milner}.

>>>>

The main change we make to PCP is \emph{removing commuting conversions} and defining an operational semantics based on structural congruence. Commuting conversions are necessary if we want our reduction strategy to correspond \emph{exactly} to cut elimination.
However, from the perspective of process calculi, commuting conversions behave strangely: they allow an input/output action to be moved to the top of a process, thus potentially blocking actions which were previously possible (an example is given in \cref{app:commuting-conversions}). This makes CP, and Dardha and Gay's PCP~\cite{dardhagay18}, non-confluent.
As Lindley and Morris~\cite{lindleymorris15} show, all communications that can be performed \emph{with} the use of commuting conversions, can also be performed \emph{without} them, if using structural congruence.
%Consider the commuting conversion $(\kappa_{\parr})$ for $\pcp{\tm{\recv{x}{y}{P}}}$:
%\begin{mathpar}
%  (\kappa_{\parr})
%  \quad
%  \tm{\res{z}{z'}{(\ppar{\recv{x}{y}{P}}{Q})}}
%  \red
%  \tm{\recv{x}{y}{\res{z}{z'}{(\ppar{P}{Q})}}}
%\end{mathpar}
%As a result of $(\kappa_{\parr})$, $\pcp{\tm{Q}}$ becomes blocked on $\pcp{\tm{\labrecv{x}{y}}}$, and any actions $\pcp{\tm{Q}}$ was able to perform become unavailable. Consequently, CP is non-confluent:
%\begin{mathpar}
%  \setlength{\arraycolsep}{2em}
%  \begin{array}{cc}
%    \multicolumn{2}{c}{%
%    \hspace*{10ex}
%    {\tm{\res{x}{x'}{(\ppar{\recv{a}{y}{P}}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    \\
%    \qquad\rotatebox[origin=c]{270}{$\red\hphantom{{}^+}$}
%    &
%    \rotatebox[origin=c]{270}{$\red^+$}\qquad
%    \\
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{\res{z}{z'}{(\ppar{\close{z}{\halt}}{\wait{z'}{Q}})}})}}}}
%    &
%    {\tm{\recv{a}{y}{\res{x}{x'}{(\ppar{P}{Q})}}}}
%  \end{array}
%\end{mathpar}
%

@@

We prove closed progress for our updated PCP. The proof is in \cref{prf:thm-pcp-closed-progress}.
\begin{compacttheorems}
  \begin{restatabletheorem}{thmpcpclosedprogress}[Progress, $\pcp{\red}$]%
    \label{thm:pcp-closed-progress}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\emptyenv}}$, then either $\pcp{\tm{P}=\tm{\halt}}$ or there exists a $\pcp{\tm{Q}}$ such that $\pcp{\tm{P}\red\tm{Q}}$.
  \end{restatabletheorem}
\end{compacttheorems}
\endgroup

@@
